The pollination trade-off

### 2018-11-18 paper/manuscript.Rmd
Add some bibliography that might be useful for the discussion

>>>>

Interspecific pollen transfer is the most important factor underpining competition for pollinators [@campbell_mechanism_1985]

Traits are determined by competition for pollination -- Caruso 2000

, all while accounting for the traits of the species that integrate the community.  extent to which plants employ  relative contribution and the interplay of each factor requires
First, that plants might use different strategies to reduce competition for pollination. 
Second that the effect of coorelated factors in the quality and quantity of pollination [like generalism, its relative abundance, and visitation frequency; @sargent_role_2006] might balance each other.

Interspecific pollen transfer was responsible for reduction in set set for one species but loss of conspecific pollen was responsible for another -- Campbell and Motten 1985

Plant species vary greatly on the extent to which each of these two mechanisms can affect fertilisation [@campbell_mechanism_1985], a large plant

Competition can also be mediated by pollinator density, not just plant density [@ye_competition_2014]

Check @flanagan_effects_2011 for discussion on the effects when one thinks about communities.

Traits can have a role only with High abundances, where being dominant can be bad for other plants in communities. Abbundance is important in small species number systems [@munoz_presence_2008]

Plants have mechanishms that prevent heterospecific pollen deposition. @bartomeus_high_2008 show that even when a plant dominates the pollen transfer network opther species might not receive lots of heterospecific pollen [@bartomeus_high_2008; @flanagan_increased_2010]

Pollen limitation is inversely related to abundance, but high abundance is also related to mate limitation [@moeller_facilitative_2004]

Competition also depends on the spatial extent [@cariveau_spatially_2009]

Facilitation is still controversial? [@feldman_when_2004]
